---
title: 'Appendix: Tables of Model Summaries'
author: "C. Taff, C. Zimmer, J. Uehling, T. Ryan, D. C. van Oordt, A. Injaian, M. Vitousek"
date: "Last Updated: `r format(Sys.time(), '%B %d %Y at %H:%M')`"
output: 
  html_document:
    toc: true
    theme: cosmo
---

```{r setup, include=FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sjPlot)
```

## **Female Measures: Mass, Physiology, Microbiome**

### **Table A1.** Female mass in relation to treatment for experiment one.

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_mass_18b_t.RDS"))
m
```
 
 
### **Table A2.** Female mass in relation to treatment for experiment two.

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_mass_19b_t.RDS"))
m
```

 
### **Table A3.** Female corticosterone in relation to treatment in experiment one.

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_18_cort_t.RDS"))
m
```
 
### **Table A4.** Female corticosterone in relation to treatment in experiment two.

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_19_cort_t.RDS"))
m
```

### **Table A5.** Female glucose in relation to treatment for experiment one.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_18_gluc_t.RDS"))
m
```


### **Table A6.** Female glucose in relation to treatment for experiment two.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_19_gluc_t.RDS"))
m
```


### **Table A7.** Female microbiome diversity in relation to treatment for experiment one.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_micro_18_t.RDS"))
m
```


### **Table A8.** Female microbiome diversity in relation to treatment for experiment two.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_micro_19_t.RDS"))
m
```


## **Female Behavior: Provisioning**

### **Table A9.** Female provisioning behavior in relation to treatment for experiment one.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_feed18_t.RDS"))
m
```
### **Table A10.** Female provisioning behavior in relation to treatment for experiment two.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_feed19_t.RDS"))
m
```

## **Female Behavior: Visitation Patterns**

### **Table A11.** Social interactions in relation to treatment for experiment one during stage 1. 

STAGE ONE: Between first and second capture; only first stage of treatment applied. Incidince Rate Ratio values near 1 indicate no difference from baseline. Value below one indicate lower incidence rate and values above one indicate higher incidence rate.  

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_soc_18_st1_t.RDS"))
m
```
 
### **Table A12.** Social interactions in relation to treatment for experiment one during stage 2. 

STAGE TWO: After second capture; both treatments active. Incidince Rate Ratio values near 1 indicate no difference from baseline. Value below one indicate lower incidence rate and values above one indicate higher incidence rate. 

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_soc_18_st2_t.RDS"))
m
```

### **Table A13.** Social interactions in relation to treatment for experiment two during stage 1. 

STAGE ONE: Between first and second capture; only first stage of treatment applied. Incidince Rate Ratio values near 1 indicate no difference from baseline. Value below one indicate lower incidence rate and values above one indicate higher incidence rate.  

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_soc_19_st1_t.RDS"))
m
```
 
### **Table A14.** Social interactions in relation to treatment for experiment two during stage 2. 

STAGE TWO: After second capture; both treatments active. Incidince Rate Ratio values near 1 indicate no difference from baseline. Value below one indicate lower incidence rate and values above one indicate higher incidence rate. 

```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_soc_19_st2_t.RDS"))
m
```

## **Nestling Measures: Mass and Corticosterone**

### **Table A15.** Nestling mass and morphology in relation to treatment for experiment one.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m18_nest_morph_t.RDS"))
m
```


### **Table A16.** Nestling mass and morphology in relation to treatment for experiment two.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m19_nest_morph_t.RDS"))
m
```


### **Table A17.** Nestling corticosterone in relation to treatment for experiment one.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m18_nest_cort_t.RDS"))
m
```


### **Table A18.** Nestling corticosterone in relation to treatment for experiment two.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m19_nest_cort_t.RDS"))
m
```



## **Reproductive Success**

### **Table A19.** Reproductive success in relation to treatment for experiment one.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_RS_18_t.RDS"))
m
```

### **Table A20.** Reproductive success in relation to treatment for experiment two.
```{r, echo = FALSE}
m <- readRDS(here::here("5_other_outputs/m_RS_19_t.RDS"))
m
```



